Supplementary Files

### 2017-12-19 Source/Figures/paper_figures.Rmd
Update codes after submission of paper revision

## Import library
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(reshape2)
library(svglite)
```

@@

# figure_file_suffix <- ".tiff"
# figure_file_suffix <- ".svg"
figure_file_suffix <- ".pdf"
options <- commandArgs(trailingOnly = TRUE)

source( file.path( local_base_directory, "./Common/parameters_file.R") ) 
source( file.path ( source_directory_common, 'count_triplet_motifs_helper.R'))
source( file.path ( local_base_directory, './Figures/paper_figures_helper.R') )

@@

@@

## Figure 2b. Six over-represented triplet motifs
```{r}

### Print the analysis of negative genetic interactions 
negative_interactions_full     <- read.table ( file= file.path( computational_results_directory, 
											   "Negative_Genetic_Interactions/Final_Results/full_results_triplet_motifs_costanzo_2016_collated.tab") )

@@

@@

>>>>

## Import library
```{r}

# install.packages( 'ggpubr')
library(dplyr)
library(tidyr)
library(ggplot2)
library(reshape2)
library(svglite)
library(ggpubr)
```

@@

# 
# figure_file_suffix <- ".tiff"
# figure_file_suffix <- ".svg"
figure_file_suffix <- ".pdf"
options <- commandArgs(trailingOnly = TRUE)

local_base_directory <- "/home/ignatius/PostDoc/2016/Triplet_Motifs/Source"
source( file.path( local_base_directory, "./Common/parameters_file.R") ) 
source( file.path ( source_directory_common, 'count_triplet_motifs_helper.R'))
source( file.path ( source_directory, './Figures/paper_figures_helper.R') )

@@

## Analyze how filtering the negative genetic interaction by the stringency in fitness score affects the six types of triplet motifs. 
```{r}

full_results_file_list   <- Sys.glob ( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/More_stringent*/Final_Results/full*")
random_results_file_list <- Sys.glob ( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/More_stringent*/Final_Results/random*")

list_of_percentiles <- as.numeric( gsub( ".*More_stringent_network_(\\d+).*", "\\1", full_results_file_list) )

observed_results_file_list <- map_chr( list_of_percentiles,
	 function(x) { 
	 		paste( "/home/ignatius/PostDoc/2016/Triplet_Motifs/Results/Bootstrap_p_values/More_stringent_network_", x,"/Job_", 
	 		   		(x / 5*20),"/results_count_triplet_motifs_costanzo.tab", sep="") 
	 	 })

input_list <- list( full_results_file_list, 
			 random_results_file_list, 
			 observed_results_file_list)

## Test length of inpu
map ( input_list, length)

results_list <- combine_graphs_using_faceting ( input_list, list_of_percentiles, sort_facet_decreasing=TRUE)

is_significant_tidy <- results_list$is_significant
observed_data_tidy <- results_list$observed_data
random_data_tidy <- results_list$random_data

 significance_color <- sapply ( is_significant_tidy[,"is_significant"], function(x) {  return(boolean_to_colour(x)) } )

 background_colour <- "white"

	return_plot <- ggplot(random_data_tidy, aes(facet_type, value)) + 
			geom_boxplot() + 
			geom_point( data=observed_data_tidy, aes(x=facet_type, y=value  )   ## Add the observed values as additional points
						, color=significance_color, size=2 , alpha=0.5) 	+ # , size=4 , alpha=0.5
			xlab( "Percentage of Negative Genetic Interactions") 	+ 
			ylab( "Counts")  + 
			facet_grid( key ~., scales="free") +
			theme( plot.background = element_rect(fill = background_colour, color=background_colour), 
				   axis.text = element_text(colour = axis_text_colour),
				   axis.title = element_text(colour = axis_text_colour),
				   strip.text.y=element_text(face="italic"))

	ggsave(file.path(figures_results_directory, paste( "more_stringent_network_all", figure_file_suffix, sep="") ), 
	   plot=return_plot, width=graphic_width, 
	   height=graphic_height*2 )

@@

## Figure 2b. Six over-represented triplet motifs
```{r}
### Print the analysis of negative genetic interactions 
negative_interactions_full     <- read.table ( file= file.path( computational_results_directory, 
											   "Negative_Genetic_Interactions/Final_Results/full_results_triplet_motifs_costanzo_2016_collated.tab") )

@@

## The maximum number of overlapping triplets for each gi to show (e.g. highest nubmer of overlaps)
statistical_analysis <- dplyr::filter( statistical_analysis, counts <= max_num_overlapping_triplets_to_show)

@@

## Supplementary Figure 1. Frequency of triplet motifs where all three proteins in the triplet share the same GO slim term.
```{r}

full_results_file_list <- Sys.glob ( paste ( computational_results_directory, 
										 "/GO_Terms_*/Final_Results/full_results_table_*_in_tri_motifs.tab", sep="")  )

random_results_file_list <- Sys.glob ( paste( computational_results_directory, 
																 "/GO_Terms_*/Final_Results/randomized_counts_*_in_tri_motifs.tab", sep=""  ) )

observed_results_file_list <- Sys.glob ( paste( computational_results_directory, 
																"/GO_Terms_*/Job_20/observed_counts_go_terms*_in_tri_motifs.tab", sep="" ))

list_of_go_types <- factor( c("Biological\nProcess", "Cellular\nComponent", "Molecular\nFunction") )

input_list <- list( full_results_file_list, 
			 random_results_file_list, 
			 observed_results_file_list)

## Test number of input files in each element of the 'input_list' object, 
## They should all have the same length
map ( input_list, length)

output_file_name <- file.path(figures_results_directory, paste( "significant_gene_ontology_all", figure_file_suffix, sep="") )

result_list <- combine_graphs_using_faceting ( input_list, list_of_go_types, sort_facet_decreasing=FALSE)

motif_type_significance_box_plot_vertical_stack_faceting( result_list$observed_data, 
														  result_list$random_data, 
														  result_list$is_significant, 
														  output_file_name, graphic_width, graphic_height*2)

## Supplementary Figure 2. Frequency of triplet motifs where all three proteins in the triplet share the same phenotype annotation. 
```{r}

### Print the analysis of negative genetic interactions 
negative_interactions_full     <- read.table ( file= file.path( computational_results_directory, 
											   "Phenotype/Final_Results/full_results_table_phenotypes_in_tri_motifs.tab") )

negative_interactions_random   <- read.table ( file=  file.path( computational_results_directory, 
																 "Phenotype/Final_Results/randomized_counts_phenotypes_in_tri_motifs.tab"  ))

negative_interactions_observed <- read.table ( file= file.path( computational_results_directory, 
																"Phenotype/Job_20/observed_counts_phenotypes_in_tri_motifs.tab"), 
								               header=TRUE )

ggsave(file.path(figures_results_directory, paste( "significant_Phenotype", figure_file_suffix, sep="") ), 
	   plot=last_plot(), width=graphic_width, 
	   height=graphic_height )

### 2017-12-19 Source/Supplementary_Files/supplementary_files.Rmd
Update codes after submission of paper revision

@@

@@

## Interactions that are from triplet motifs only
```{r}

>>>>

## Table list all triplets where the genetic interactions overlap with other types of interactions 
triplets_gi_overlapping_other_edges <- read.table( file.path(supplementary_data_directory, "triplets_with_overlapping_edges.tab"), 
										header=TRUE, sep="\t", stringsAsFactors = FALSE, quote="" )

## List of GO terms shared by all three proteins in the triplet 
## The tables need t be pre-computed by the script: "GO_terms/count_go_terms.R"
shared_go_terms_BP_per_triplet <- read.table( file.path(supplementary_data_directory, "shared_go_terms_BP_per_triplet.tab"), 
										header=TRUE, sep="\t", stringsAsFactors = FALSE, quote="" )
shared_go_terms_CC_per_triplet <- read.table( file.path(supplementary_data_directory, "shared_go_terms_CC_per_triplet.tab"), 
										header=TRUE, sep="\t", stringsAsFactors = FALSE, quote="" )
shared_go_terms_MF_per_triplet <- read.table( file.path(supplementary_data_directory, "shared_go_terms_MF_per_triplet.tab"), 
										header=TRUE, sep="\t", stringsAsFactors = FALSE, quote="" )

## List of phenotypes shared by all three proteins in the triplet 
## Phenotype data obtained from SGD.
## This table needs to be pre-computed by the script 'Phenotype/count_triplets_with_same_phenotype.R'
triplet_shared_phenotype <- read.table( file.path(supplementary_data_directory, "motif_and_phenotypes_detail.txt"), 
										header=TRUE, sep="\t", stringsAsFactors = FALSE, quote="" )

@@

## Calculate the number of other triplets sharing this negative genetic interactions
num_of_overlapping_triplets_table <-  densely_annotated_triplet_motif %>%
								dplyr::select ( one_of ( c( "oln_id_a", "oln_id_b", "oln_id_c", 
															"type_of_interaction_a_to_c", "type_of_interaction_b_to_c" ))) %>%
								dplyr::group_by( oln_id_a, oln_id_b) %>%
								# Remember that we need to minus one here to exclude itself from the count
								dplyr::summarise( num_of_other_triplets_sharing_this_genetic_interaction = n() - 1) %>% 
								dplyr::ungroup()

densely_annotated_triplet_motif <- sqldf( " select x.*
											, coalesce( overlap.P, 0) as P
											, coalesce( overlap.K1, 0) as K1
											, coalesce( overlap.K2, 0) as K2
											, coalesce( overlap.T1, 0) as T1	
											, coalesce( overlap.T2, 0) as T2
											, coalesce( repeated_gi.num_of_other_triplets_sharing_this_genetic_interaction, 0) 
                                   					as num_of_other_triplets_sharing_this_genetic_interaction
											, coalesce(w_bp.go_BP_count, 0 ) as num_go_BP_shared
											, w_bp.go_BP_intersect_abc
											, coalesce(w_cc.go_CC_count, 0 ) as num_go_CC_shared
											, w_cc.go_CC_intersect_abc
											, coalesce(w_mf.go_MF_count, 0 ) as num_go_MF_shared
											, w_mf.go_MF_intersect_abc
											, coalesce(y.num_phenotype_shared, 0) num_phenotype_shared
											, y.phenotype_intersect_abc
										    from densely_annotated_triplet_motif x
												 left join triplets_gi_overlapping_other_edges overlap 
												   on  x.oln_id_a = overlap.oln_id_a
														and x.oln_id_b = overlap.oln_id_b
														and x.oln_id_c = overlap.oln_id_c 
														and x.type_of_interaction_a_to_c = upper(overlap.type_ac)
														and x.type_of_interaction_b_to_c = upper(overlap.type_bc)
												 left join num_of_overlapping_triplets_table repeated_gi
													on x.oln_id_a = repeated_gi.oln_id_a
														and x.oln_id_b = repeated_gi.oln_id_b
												 left join shared_go_terms_BP_per_triplet  w_bp
										  			on  x.oln_id_a = w_bp.oln_id_a
														and x.oln_id_b = w_bp.oln_id_b
														and x.oln_id_c = w_bp.oln_id_c 
														and x.type_of_interaction_a_to_c = upper(w_bp.type_ac)
														and x.type_of_interaction_b_to_c = upper(w_bp.type_bc)
												 left join shared_go_terms_CC_per_triplet  w_cc
										  			on  x.oln_id_a = w_cc.oln_id_a
														and x.oln_id_b = w_cc.oln_id_b
														and x.oln_id_c = w_cc.oln_id_c 
														and x.type_of_interaction_a_to_c = upper(w_cc.type_ac)
														and x.type_of_interaction_b_to_c = upper(w_cc.type_bc)
												 left join shared_go_terms_MF_per_triplet  w_mf
										  			on  x.oln_id_a = w_mf.oln_id_a
														and x.oln_id_b = w_mf.oln_id_b
														and x.oln_id_c = w_mf.oln_id_c 
														and x.type_of_interaction_a_to_c = upper(w_mf.type_ac)
														and x.type_of_interaction_b_to_c = upper(w_mf.type_bc)
										  		 left join triplet_shared_phenotype y
										  			on  x.oln_id_a = y.oln_id_a
														and x.oln_id_b = y.oln_id_b
														and x.oln_id_c = y.oln_id_c 
														and x.type_of_interaction_a_to_c = upper(y.type_ac)
														and x.type_of_interaction_b_to_c = upper(y.type_bc)
														 ")

@@

## Interactions that are part of triplets, excluding those that are not part of triplets
```{r}
